Democracy, Public Support, and Measurement Uncertainty

### 2021-04-29 paper/dcpo_demsupport.Rmd
figuring the country-year matching in `claassenUnicertaintyAJPS`

ls_mod <-
  paste0(
    "Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + ",
    c(
      "plm::lag(SupDem_trim, 1)",
      "plm::lag(SupDem_Democ, 1) + plm::lag(SupDem_Autoc, 1)"
    ),
    "+ plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)"
  )

@@

```{r claassenUncertaintyAJPS}

@@

```{r dcpoPointAJPS}
ls_country <- levels(dcpo_input$data$kk)
first_year <- min(dcpo_input$data$year)

@@

```{r claassenAPSR}
sd.plm <- pdata.frame(x, index = c("Country", "Year"))

mods <- vector(mode = "list")

mods[[1]] <- plm(
  diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Libdem_z, lag = 1)
  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1),
  sd.plm,
  model = "pooling"
)
mods[[2]] <- plm(
  diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Libdem_z, lag = 1)
  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)
  + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1),
  sd.plm,
  model = "pooling"
)

@@

save(df_result_clsAPSR, file = here::here("output", "estimates_clsMeanAPSR.RDS"))
```

>>>>

@@

```{r claassenUncertaintyAJPS}
claassen_replication_input$data <- claassen_replication_input$data %>% 
  janitor::clean_names() %>% 
  DCPOtools::with_min_yrs(2)

@@

```{r dcpoPointAJPS}

ls_country <- levels(dcpo_input$data$kk)
first_year <- min(dcpo_input$data$year)

@@

```{r claassenAPSR}
df_result_cls <- map(ls_mod, function(mod) {
  result <- eval(parse(text = mod))
})

sd.plm <- pdata.frame(x, index = c("Country", "Year"))

ls_mods <- vector(mode = "list")

ls_mods[["ECM1.1"]] <- plm(
  diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Libdem_z, lag = 1)
  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1),
  data = sd.plm,
  model = "pooling"
)

ls_mods[["ECM1.2"]] <- plm(
  diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Libdem_z, lag = 1)
  + plm::lag(Libdem_z, 1) + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)
  + diff(Corrup_TI_z, lag = 1) + plm::lag(Corrup_TI_z, 1),
  data = sd.plm,
  model = "pooling"
)

ls_mods[["FD1.1"]] <-
  plm(
    SupDem_trim ~ Libdem_z + lnGDP_imp,
    model = "fd",
    data = sd.plm,
    index = "Country"
  )

ls_mods[["FD1.2"]] <-
  plm(
    SupDem_trim ~ Libdem_z + lnGDP_imp + Corrup_TI_z,
    model = "fd",
    data = sd.plm,
    index = "Country"
  )

ls_mods[["ECM2.1"]] <-
  plm(
    diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Polyarchy_z, lag = 1)
    + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)
    + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1),
    sd.plm,
    model = "pooling"
  )
ls_mods[["FD2.1"]] <-
  plm(
    diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + diff(Polyarchy_z, lag = 1)
    + plm::lag(Polyarchy_z, 1) + diff(Liberal_z, lag = 1) + plm::lag(Liberal_z, 1)
    + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1) + diff(Corrup_TI_z, lag = 1)
    + plm::lag(Corrup_TI_z, 1),
    sd.plm,
    model = "pooling"
  )

# FD models

ls_mods[["ECM2.2"]] <-
  plm(
    SupDem_trim ~ Polyarchy_z + Liberal_z + lnGDP_imp,
    model = "fd",
    data = sd.plm,
    index = "Country"
  )
ls_mods[["FD2.2"]] <-
  plm(
    SupDem_trim ~ Polyarchy_z + Liberal_z + lnGDP_imp + Corrup_TI_z,
    model = "fd",
    data = sd.plm,
    index = "Country"
  )

@@

#save(df_result_clsAPSR, file = here::here("output", "estimates_clsMeanAPSR.RDS"))
```
